---
title: "GACE: Generalized Adaptive Capped Estimator"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{GACE: Generalized Adaptive Capped Estimator}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Introduction

The **GACE** package provides a fast, deterministic, and interpretable
forecasting method based on hybrid growth signals and asymmetric caps.
It supports weekly, monthly, quarterly, and yearly data and allows users
to choose manual or automatic cap selection.

This vignette illustrates basic usage of the package.

# Basic example

```{r setup}
library(GACE)
```

We begin by generating a simple monthly time series:

```{r}
set.seed(123)
y <- ts(rnorm(36, 100, 10), frequency = 12)
```

Now we produce a 12-month forecast:

```{r}
fc <- gace_forecast(
  df = y,
  periods = 12,
  freq = "month",
  seasonal = TRUE
)

head(fc)
```

# Plotting

```{r}
plot_gace(fc)
```

# How it works

GACE blends three intuitive growth signals:

- year-over-year growth  
- prior-period growth  
- rolling-window growth  

It then applies fixed or adaptive asymmetric caps to ensure
non-explosive forecasts and optional seasonal scaling.

# Conclusion

GACE provides a practical, transparent forecasting alternative for
business and applied analytics.  
For more details, refer to the function documentation.
